---
title: "Untitled"
output: html_document
date: '2022-06-30'
editor_options: 
  chunk_output_type: console
---

# Workspace  
## Packages  
```{r packages}
library(psych)
library(knitr)
library(kableExtra)
library(lubridate)
library(cowplot)
library(plyr)
library(tidyverse)
library(brms)
```

## Directory  
```{r}
wd <- "/Volumes/Emorie/projects/linking-change"
```

## Codebook  
```{r}
esm_codebook <- sprintf("%s/02-codebooks/Codebook.csv", wd) %>% 
  read_csv() %>% 
  filter(type == "ESM") 

trait_codebook <- sprintf("%s/02-codebooks/Codebook.csv", wd) %>% 
  read_csv() %>% 
  filter(type != "ESM") 
```

# Data  
## ESM Data  
```{r ESM data, results='hide'}
subs <- sprintf("%s/01-data/01-raw-data/01-esm/subs.csv", wd) %>% read_csv()

wave1_all <- sprintf("%s/01-data/01-raw-data/01-esm/esm_w1_RENAMED.csv",     wd) %>% 
  read_csv() %>%
  select(one_of(paste(esm_codebook$old_name, "w1", sep = "."))) %>%
  mutate(esm.IDnum.w1 = as.character(mapvalues(esm.IDnum.w1, subs$old, subs$new, warn_missing = F)))
wave4_all <- sprintf("%s/01-data/01-raw-data/01-esm/esm_w4_RENAMED_all.csv", wd) %>% 
  read_csv() %>%
  select(one_of(paste(esm_codebook$old_name, "w4", sep = "."))) %>%
  mutate(esm.IDnum.w4 = as.character(mapvalues(esm.IDnum.w4, subs$old, subs$new, warn_missing = F))) 
wave7_all <- sprintf("%s/01-data/01-raw-data/01-esm/esm_w7_RENAMED_all.csv", wd) %>% 
  read_csv() %>%
  select(one_of(paste(esm_codebook$old_name, "w7", sep = "."))) %>%
  mutate(esm.IDnum.w7 = as.character(mapvalues(esm.IDnum.w7, subs$old, subs$new, warn_missing = F))) 

old.names <- esm_codebook$old_name
new.names <- esm_codebook$new_name

#Getting necessary columns
#Keeping subject ID and all esm.BFI items
w1 <- wave1_all %>%
  select(one_of(paste(old.names, "w1", sep = "."))) %>%
  setNames(new.names) %>% # change column names
  mutate(wave = "S1") 
w4 <- wave4_all %>%
  select(one_of(paste(old.names, "w4", sep = "."))) %>%
  setNames(new.names) %>% # change column names
  mutate(wave = "S4")
w7 <- wave7_all %>%
  select(one_of(paste(old.names, "w7", sep = "."))) %>%
  setNames(new.names) %>% # change column names
  mutate(wave = "S7")

w1 <- w1 %>%
  group_by(SID) %>%
  arrange(day, hourBlock) %>%
  mutate(beep_seq = seq(1, n(), 1)) %>%
  ungroup()
```

### MI  
```{r}
w1_mi <- data.frame(unclass(w1 %>% select(-freq, -hourBlock, -day, -beep_seq, -wave)))
set.seed(5)
w1 <- amelia(w1_mi, m = 1, ts = "beepvar", cs = "SID")$imputations[[1]] %>%
  as_tibble() %>%
  full_join(w1 %>% select(SID, beepvar, wave)); w1_mi

w4_mi <- data.frame(unclass(w4 %>% select(-freq, -hourBlock, -day, -wave)))
set.seed(12)
w4 <- amelia(w4_mi, m = 1, ts = "beepvar", cs = "SID")$imputations[[1]] %>%
  as_tibble() %>%
  full_join(w4 %>% select(SID, beepvar, wave)); w4_mi

w7_mi <- data.frame(unclass(w7 %>% select(-freq, -hourBlock, -day, -wave)))
set.seed(176)
w7 <- amelia(w7_mi, m = 1, ts = "beepvar", cs = "SID")$imputations[[1]] %>%
  as_tibble() %>%
  full_join(w7 %>% select(SID, beepvar, wave)); w7_mi
```


## Trait Data  
Now we get the 7 waves of trait level data. In the data file, the items were given an adjective descriptor rather than one that matched the trait and item number in the original BFI. So I create a data frame that does that so I can get this information easily.  
## Rename and Reshape  
```{r trait data}
# make vectors of the original names of the data and the new names I'll give them for ease of use
old_cols <- c("talkative", "findfault", "thorough", "depressed", "original", "reserved", "helpful",
          "careless", "relaxed", "curious", "energy", "quarrels", "reliable", "tense", "ingenious",
          "enthusiasm", "forgiving", "disorganized", "worries", "imagination", "quiet", "trusting",
          "lazy", "emotionallystable", "inventive", "assertive", "cold", "perseveres", "moody", 
          "artistic", "shy", "considerate", "efficient", "calm", "routine", "outgoing", "rude",
          "plans", "nervous", "reflect", "unartistic", "cooperate", "distracted", "sophisticated")

new_cols <- c(paste(rep(c("E", "A", "C", "N", "O"), times = 8), 
              rep(seq(1,8,1), each = 5), sep = "_"), 
              "O_9", "A_9", "C_9", "O_10")

cols <- tibble(old = old_cols, new = new_cols)

# load data and rename items to match the original BFI
trait_data <- sprintf("%s/01-data/01-raw-data/02-trait/sevenwaves_REDACTED.csv", wd) %>% 
    read.csv() %>%
    # mutate(id = as.character(mapvalues(id, subs$old2, subs$new))) %>%
    pivot_longer(
      names_to = "item"
      , values_to = "value"
      , cols = outgoing1:sophisticated_d
      , values_drop_na = T
    ) %>%
    mutate(item = gsub("[_]", "", item)) %>%
    separate(item, c("item", "wave"), -1) %>%
    filter(!(item %in% c("connected", "likesothers"))) %>%
    mutate(item = factor(mapvalues(item, from = old_cols, to = new_cols), levels = new_cols),
           wave = mapvalues(wave, from = c("1", "a", "b", "2", "c", "d", "3"),
                            to = paste("T", seq(1,7,1), sep = ""))) %>%
    rename(SID = id) %>%
    select(SID, wave, item, value)
```

### Reverse Code  
```{r reverse code trait}
(trait_data <- trait_data %>%
    left_join(trait_codebook %>% select(item = new_name, rev_code)) %>%
    mutate(value = ifelse(rev_code == 1, reverse.code(-1, value, mini = 1, maxi = 15), value)) %>%
    select(-rev_code))
```

### Cronbach's Alpha  
```{r alpha}
alpha_fun <- function(df){
  df <- df %>% select(-SID)
  psych::alpha(df)$total$raw_alpha
}

# calculate scale reliabilities for trait data
trait_alphas <- trait_data %>%
  mutate(SID = as.character(SID)) %>%
  separate(item, c("trait", "item"), sep = "_") %>%
  group_by(wave, trait) %>%
  nest() %>% 
  ungroup() %>%
  mutate(data = map(data, ~(.) %>% 
                      pivot_wider(
                        names_from = "item"
                        , values_from = "value"
                      ))
         , alpha = map_dbl(data, alpha_fun)) %>%
  select(-data) %>%
  spread(key = trait, value = alpha) 

trait_alphas %>%
  kable(., "html", booktabs = T, digits = 2,
        caption = "Cronbach's Alpha for Trait-Level Scales") 

# target.esm.subs <- esm_subs %>% full_join(target_subs)
```

### Trait Composites  
```{r trait composites}
# estimate trait composites for each wave
trait_comp <- trait_data %>%
  separate(item, c("trait", "item"), sep = "_") %>%
  group_by(SID, wave, trait) %>%
  summarize(t_value = mean(value, na.rm = T)) %>%
  group_by(SID, trait) %>%
  mutate(wave = as.numeric(str_remove(wave, "T"))
         , wave_c = wave - min(wave)) %>%
  ungroup() 
```


```{r item-level profile correlations}
trait_rs <- trait_data %>%
  mutate(wave = as.numeric(str_remove(wave, "T"))) %>%
  arrange(SID, item, wave) %>%
  group_by(SID, item) %>%
  filter(lead(wave) - wave == 1 | wave - lag(wave) == 1) %>%
  mutate(value2 = lead(value)
         , wave2 = paste(wave, lead(wave), sep = "_")) %>%
  filter(lead(wave) - wave == 1) %>%
  group_by(SID, wave2) %>%
  summarize(r = cor(value, value2, use = "pairwise")) %>%
  ungroup() %>%
  mutate(wave = as.numeric(mapvalues(wave2, c("1_2", "2_3", "3_4", "4_5", "5_6", "6_7")
                          , c(0, 1, 2, 3, 4, 5), warn_missing = F))) %>%
  group_by(SID) %>%
  mutate(wave_c = wave - min(wave)) %>%
  ungroup()

trait_rs %>% 
  ggplot(aes(x = r)) + 
    geom_histogram(aes(y = ..density..), fill = "lightgrey", color = "black") + 
    geom_density() + 
    facet_wrap(~wave2) + 
    theme_classic()
```



# Networks  
## dynEGA  
```{r dynEGA}
ega_fun <- function(d, wave, sid){
  d <- data.frame(d)
  # get numeric ID of the participant ID column
  idcol <- which(colnames(d) == "SID2")
  gcol  <- which(colnames(d) == "wave2")
  
  ega_ind <- dynEGA(
    data = d 
    , n.embed = 4 # embedding dimension
    , tau = 1  # offset for embedding, similar to lag 1
    , delta = 4 # time between obs
    , level = "individual" # we want individual-level models 
    , id = idcol # id column position
    , group = gcol # group membership, in this case the wave
    , use.derivatives = 1 # we want to use 1st order derivatives
    , model = "glasso" 
    , model.args = list(gamma = .1)
    , algorithm = "louvain" # the clustering algorithm for structure
    , corr = "pearson" # type of correlation
    , ncores = 1 # number of cores
  ); ega_ind
  
  save(ega_ind, file = sprintf("%s/05-results/01-eganet/01-models/%s-%s.RData", wd, wave, sid))
  
  return(ega_ind$dynEGA[[1]])
}


nested_ega <- w4 %>%
  full_join(w7) %>%
  arrange(SID, wave, beepvar) %>%
  mutate(wave = "S4") %>%
  full_join(
    w1 %>%
      arrange(SID, beepvar)
    ) %>%
  group_by(SID, wave) %>%
  filter(n() >= 10) %>%
  ungroup() %>%
  select(-beepvar) %>%
  mutate(wave2 = wave
         , SID2 = as.character(SID)) %>%
  group_by(SID, wave) %>%
  nest() %>%
  ungroup() %>%
  mutate(net = pmap(list(data, wave, SID), possibly(ega_fun, NA_real_)))
```

### Entropy & Total Correlation    
```{r entropy and tc}
entropy_fun <- function(d, n){
  d <- d %>% select(-SID2, -wave2)
  wc <- n$wc
  if(any(is.na(wc))){
    missing <- which(is.na(wc))
    wc <- wc[-missing]
    d <- d[, -missing]
  }
  entropyFit(data = d, structure = wc)
}

nested_ega <- nested_ega %>%
  filter(!is.na(net)) %>%
  mutate(entropy = map2(data, net, possibly(entropy_fun, NA_real_)))
```

### Density  
```{r net density}
dens_fun <- function(n){
  net <- n$network
  net[upper.tri(net, diag = T)] <- NA
  sum(net != 0, na.rm = T)/sum(!is.na(net))
}

nested_ega <- nested_ega %>%
  filter(!is.na(net)) %>%
  mutate(density = map_dbl(net, possibly(dens_fun, NA_real_)))
```

### Cross-Wave Consistency (1-2 only)  

```{r net ip r}
r_fun <- function(d1, d2){
  c1 <- colnames(d1); c2 <- colnames(d2)
  d1 <- d1[rownames(d1) %in% c2, colnames(d1) %in% c2]
  d2 <- d2[rownames(d2) %in% c1, colnames(d2) %in% c1]
  d1[upper.tri(d1, diag = T)] <- NA; d2[upper.tri(d2, diag = T)] <- NA
  cor(c(d1), c(d2), use = "pairwise")
}

idio_ip_cors <- nested_ega %>%
  mutate(net = map(net, ~(.)$network)) %>%
  select(SID, wave, net) %>%
  pivot_wider(names_from = "wave", values_from = "net") %>%
  filter(map_lgl(S4, is.null) == F & map_lgl(S1, is.null) == F) %>%
  mutate(r = map2_dbl(S1, S4, r_fun))
```

### NMI  
```{r}
nmi_fun <- function(net){
  wc <- net$wc
  wc <- wc[!is.na(wc)]
  theoretical <- names(wc)
  theoretical <- as.numeric(as.factor(laply(str_split(theoretical, pattern = "_"), function(x) x[1])))
  names(theoretical) <- names(wc)
  
  # Match with theoretical
  matched <- theoretical[match(names(wc), names(theoretical))]
  
  igraph::compare(wc, matched, method = "nmi")
}

nested_ega <- nested_ega %>%
  mutate(nmi = map_dbl(net, possibly(nmi_fun, NA_real_)))
```

## Combine Metrics  
```{r}
idio_long <- nested_ega %>% 
  select(-data, -net, -entropy) %>%
  full_join(
    nested_ega %>% 
      select(-data, -net, -density, -nmi) %>%
      filter(!is.na(entropy)) %>% 
      unnest(entropy) %>%
      select(SID, wave, totcor = Total.Correlation, entropy = Average.Entropy)
  ) %>%
  full_join(
    idio_ip_cors %>%
      select(-S4, -S1) %>%
      mutate(wave = "S1")
  ) %>%
  arrange(SID, wave) %>%
  pivot_longer(
    names_to = "idio_index"
    , values_to = "idio_value"
    , values_drop_na = T
    , cols = density:r
  )

rm(nested_ega)
```

# Trait Trajectories  
## Merge the Data  
```{r}
d_nested <- trait_comp %>%
  mutate(SID = as.character(SID)) %>%
  full_join(
    idio_long %>% 
      rename(i_wave = wave)
  )  %>% 
  filter(!is.na(i_wave)) %>%
  group_by(trait, i_wave, idio_index) %>%
  nest() %>%
  ungroup()
```

## Sample Model  
```{r}
d <- d_nested$data[[1]]
m0 <- brm(
    t_value ~ 1 + wave_c + idio_value + wave_c:idio_value + (1 + wave_c | SID)
    , data = d
    , prior = c(prior(normal(7, 3), class = Intercept),
                                 prior(cauchy(0, .1), class = sd),
                                 prior(normal(0, .1), class = b),
                                 prior(exponential(1), class = sigma),
                                 prior(lkj(1), class = cor))
    , cores = 4
    , chains = 4
    , iter = 100
    , warmup = 10
  )
save(m0, file = sprintf("%s/05-results/trait-sample-model.RData", wd))
```

## Run the Models  
```{r}
lin_model_fun <- function(d, trait, metric, wave){
  m <- update(m0
              , newdata = d
              # , prior = c(prior(normal(.6, .1), class = Intercept)
              #             , prior(cauchy(0, .1), class = sd)
              #             , prior(normal(0, .1), class = b)
              #             , prior(exponential(1), class = sigma)
              #             , prior(lkj(1), class = cor))
              , cores = 4
              , chains = 4
              , iter = 8000
              , warmup = 3000
  )
  save(m, file = sprintf("%s/05-results/02-trait-models/01-models/%s-%s-%s.RData", wd, trait, metric, wave))
  
  fx <- tidy(m)
  rx <- coef(m)$SID %>% array_tree(3) %>% 
    tibble(term = names(.), data = .) %>%
    filter(term %in% c("Intercept", "wave_c")) %>%
    mutate(data = map(data, ~(.) %>% data.frame %>% 
                        rownames_to_column("SID"))) %>% 
    unnest(data) %>% 
    select(term, SID, estimate = Estimate, conf.low = Q2.5, conf.high = Q97.5)
  save(fx, rx, file = sprintf("%s/05-results/02-trait-models/02-summary/%s-%s-%s.RData", wd, trait, metric, wave))
  
  draws <- as_draws_df(m)
  save(draws, file = sprintf("%s/05-results/02-trait-models/03-draws/%s-%s-%s.RData", wd, trait, metric, wave))
  
  idio_levs <- d %>% 
    select(SID, idio_value) %>%
    distinct() %>%
    drop_na() %>%
    summarize(m = mean(idio_value)
              , low = m - sd(idio_value)
              , high = m + sd(idio_value))
  
  frame <- crossing(
    wave_c = 0:6
    , idio_value = c(idio_levs$low, idio_levs$m, idio_levs$high)
  ) %>%
    mutate(idio_fac = factor(idio_value, c(idio_levs$low, idio_levs$m, idio_levs$high), c("-1 SD", "M", "+1 SD"))) 
  fx_pred <- bind_cols(frame, fitted(m, newdata = frame, re_formula = NA))
  
  frame <- d %>% 
    select(SID, wave_c, idio_value) %>%
    distinct()
  rx_pred <- bind_cols(frame, fitted(m, newdata = frame))
  save(fx_pred, rx_pred, file = sprintf("%s/05-results/02-trait-models/04-pred/%s-%s-%s.RData", wd, trait, metric, wave))
  
  rm(list = ls())
  gc()
  return(T)
}

d_nested %>%
  mutate(m = pmap(list(data, trait, idio_index, i_wave), lin_model_fun))
```

```{r}
load("/Volumes/Emorie/projects/linking-change/05-results/02-trait-models/01-models/E-totcor-S4.RData")
d <- m$data
idio_levs <- d %>% 
    select(SID, idio_value) %>%
    distinct() %>%
    drop_na() %>%
    summarize(m = mean(idio_value)
              , low = m - sd(idio_value)
              , high = m + sd(idio_value))

hyp_test <- hypothesis(m
           , c("wave_c + 0.1290294*wave_c:idio_value = 0"
               , "wave_c - 0.04705358*wave_c:idio_value = 0"
               , "wave_c + 0.3051124*wave_c:idio_value = 0"))

hyp_test$hypothesis 
```


## Compile the Results  
### Tables  
```{r}
loadRData <- function(file, obj){
    #loads an RData file, and returns it
    path <- sprintf("%s/05-results/02-trait-models/02-summary/%s", wd, file)
    load(path)
    get(ls()[grepl(obj, ls())])
}

nested_fx <- tibble(file = sprintf("%s/05-results/02-trait-models/02-summary", wd) %>% list.files()) %>%
  mutate(fx = map2(file, "fx", loadRData)) %>%
  separate(file, c("trait", "idio_metric", "idio_wave"), sep = "-") %>%
  mutate(idio_wave = str_remove_all(idio_wave, ".RData")) %>%
  unnest(fx) %>%
  filter(effect == "fixed") %>% 
  mutate(sig = ifelse(sign(conf.low) == sign(conf.high), "sig", "ns"))
  # group_by(idio_metric, idio_wave) %>%
  # nest() %>%
  # ungroup()

  
tab <- nested_fx %>%
  filter(idio_metric == "totcor" & idio_wave == "S4" & trait == "E") %>%
  mutate(sig = ifelse(sign(conf.low) == sign(conf.high), "sig", "ns")) %>%
  mutate_at(vars(estimate, conf.low, conf.high), ~sprintf("%.2f", .)) %>%
  mutate(CI = sprintf("[%s, %s]", conf.low, conf.high)) %>%
  mutate_at(vars(estimate, CI), ~ifelse(sig == "sig", sprintf("<strong>%s</strong>", .), .)) %>%
  select(term, estimate, CI) %>%
  kable(.
        , "html"
        , escape = F
        , col.names = c("Term", "Est.", "CI")
        , align = c("l", "c", "c")) %>%
  kable_classic(full_width = F)

save_kable(tab, file = sprintf("%s/05-results/05-tables/tab-1.html", wd))
```

### Plots  
#### Random Effects Distributions  
```{r}
loadRData <- function(file, obj){
    #loads an RData file, and returns it
    path <- sprintf("%s/05-results/02-trait-models/02-summary/%s", wd, file)
    load(path)
    get(ls()[grepl(obj, ls())])
}

nested_rx <- tibble(file = sprintf("%s/05-results/02-trait-models/02-summary", wd) %>% list.files()) %>%
  mutate(rx = map2(file, "rx", loadRData)) %>%
  separate(file, c("trait", "idio_metric", "idio_wave"), sep = "-") %>%
  mutate(idio_wave = str_remove_all(idio_wave, ".RData")) %>%
  unnest(rx) %>%
  mutate(trait = factor(trait, c("E", "A", "C", "N", "O")
          , c("Extraversion", "Agreeableness", "Conscientiousness", "Neuroticism", "Openness"))) %>%
  group_by(idio_metric, idio_wave, term, trait) %>%
  nest() %>%
  ungroup()
```

```{r}
rx_est_fun <- function(d, trait){
  ord <- (d %>% arrange(desc(estimate)))$SID
  d %>%
    mutate(SID = factor(SID, levels = ord)
           , sig = ifelse(sign(conf.low) == sign(conf.high), "sig", "ns")) %>%
    ggplot(aes(x = SID, y = estimate)) + 
      geom_errorbar(aes(ymin = conf.low, ymax = conf.high)
                    , position = "dodge"
                    , width = 0
                    , size = .25) +
      geom_point(size = .5) + 
      labs(x = "SID"
           , y = "Estimated Trait Level"
           , title = trait) +
      coord_flip() + 
      theme_classic() + 
      theme(legend.position = "bottom"
            , plot.title = element_text(face = "bold", hjust = .5)
            , axis.text.y = element_blank())
}

nested_rx_plots <- nested_rx %>%
  mutate(p = map2(data, trait, rx_est_fun)) %>%
  group_by(idio_metric, idio_wave, term) %>%
  nest() %>% 
  ungroup()

comb_trait_plot_fun <- function(d){
  d <- d %>% arrange(trait)
  p1 <- d$p[[1]]; p2 <- d$p[[2]]; p3 <- d$p[[3]]; p4 <- d$p[[4]]; p5 <- d$p[[5]]
  p1 <- p1 +  labs (y = " "); p2 <- p2 +  labs (y =" ")
  p4 <- p4 +  labs (y = " "); p5 <- p5 +  labs (y = " ")
  plot_grid(p1, p2, p3, p4, p5
            , nrow = 1
            , axis = "tb"
            , align = "v")
}

nested_rx_plots <- nested_rx_plots
```


#### Trajectories  
##### Fixed  
```{r}
loadRData <- function(file, obj){
    #loads an RData file, and returns it
    path <- sprintf("%s/05-results/02-trait-models/04-pred/%s", wd, file)
    load(path)
    get(ls()[grepl(obj, ls())])
}

nested_pred <- tibble(file = sprintf("%s/05-results/02-trait-models/04-pred", wd) %>% list.files()) %>%
  mutate(pred_fx = map2(file, "fx_pred", loadRData)) %>%
  separate(file, c("trait", "idio_metric", "idio_wave"), sep = "-") %>%
  mutate(idio_wave = str_remove_all(idio_wave, ".RData")) %>%
  unnest(pred_fx) 
```

```{r}
trait_traj_fun <- function(d, metric, wave){
  p <- d %>%
    mutate(trait = factor(trait, c("E", "A", "C", "N", "O")
                          , c("Extraversion", "Agreeableness", "Conscientiousness", "Neuroticism", "Openness"))) %>%
    ggplot(aes(x = wave_c + 1, y = Estimate, group = idio_fac)) + 
      geom_ribbon(aes(ymin = `Q2.5`, ymax = `Q97.5`, fill = idio_fac), alpha = .1) + 
      geom_line(aes(linetype = idio_fac, color = idio_fac)) + 
      scale_x_continuous(
        limits = c(1,7)
        , breaks = seq(1, 7)
      ) +
      labs(
        x = "Wave"
        , y = "Estimated Trait Level"
        , color = "Density"
        , fill = "Density"
        , linetype = "Density"
        ) + 
      facet_wrap(~trait) +
      theme_classic() + 
    theme(
      strip.background = element_rect(fill = "black")
      , strip.text = element_text(face = "bold", color = "white", size = rel(1.2))
      , legend.text = element_text(face = "bold")
      , legend.position = c(.85, .25)
      , legend.title = element_text(face = "bold")
      , axis.text = element_text(face = "bold")
      , axis.title = element_text(face = "bold")
    )
  ggsave(p
         , file = sprintf("%s/05-results/04-plots/01-trait/01-trajectories/%s-%s.png"
                          , wd, metric, wave)
         , width = 8
         , height = 6)
  ggsave(p
         , file = sprintf("%s/05-results/04-plots/01-trait/01-trajectories/%s-%s.pdf"
                          , wd, metric, wave)
         , width = 8
         , height = 6)
  return(p)
}

nested_pred_gr_plots <- nested_pred %>%
  group_by(idio_metric, idio_wave) %>%
  nest() %>%
  ungroup() %>%
  mutate(p_traj = pmap(list(data, idio_metric, idio_wave), trait_traj_fun))
```

```{r}
sing_trait_traj_fun <- function(d, trait, metric, wave){
  lim <- c(floor(min(d$Estimate)-1.5), ceiling(max(d$Estimate) + 1.5))
  p <- d %>%
    ggplot(aes(x = wave_c + 1, y = Estimate, group = idio_fac)) + 
      geom_ribbon(aes(ymin = `Q2.5`, ymax = `Q97.5`, fill = idio_fac), alpha = .25) + 
      geom_line(aes(linetype = idio_fac), color = "black", size = .6) + 
      scale_x_continuous(
        limits = c(1,7)
        , breaks = seq(1, 7)
      ) +
      scale_y_continuous(
        limits = lim
        , breaks = seq(lim[1], lim[2], 2)
      ) +
      labs(
        x = "Wave"
        , y = "Estimated Trait Level"
        # , color = metric
        , fill = metric
        , linetype = metric
        ) + 
      theme_classic() + 
    theme(
      strip.background = element_rect(fill = "black")
      , strip.text = element_text(face = "bold", color = "white", size = rel(1.2))
      , legend.text = element_text(face = "bold")
      , legend.position = "bottom"
      , legend.title = element_text(face = "bold")
      , axis.text = element_text(face = "bold")
      , axis.title = element_text(face = "bold")
      , panel.background = element_rect(color = "black", size = rel(3))
    )
  ggsave(p
         , file = sprintf("%s/05-results/04-plots/01-trait/01-trajectories/single-traits/%s-%s-%s.png"
                          , wd, trait, metric, wave)
         , width = 7
         , height = 4)
  ggsave(p
         , file = sprintf("%s/05-results/04-plots/01-trait/01-trajectories/single-traits/%s-%s-%s.pdf"
                          , wd, trait, metric, wave)
         , width = 7
         , height = 4)
  return(p)
}


nested_pred_plots <- nested_pred %>%
    mutate(trait = factor(trait, c("E", "A", "C", "N", "O")
                          , c("Extraversion", "Agreeableness", "Conscientiousness", "Neuroticism", "Openness"))) %>%
  group_by(idio_metric, idio_wave, trait) %>%
  nest() %>%
  ungroup() %>%
  mutate(p_traj = pmap(list(data, trait, idio_metric, idio_wave), sing_trait_traj_fun))
```

##### Random  
```{r}
loadRData <- function(file, obj){
    #loads an RData file, and returns it
    path <- sprintf("%s/05-results/02-trait-models/04-pred/%s", wd, file)
    load(path)
    get(ls()[grepl(obj, ls())])
}

nested_pred_rx <- tibble(file = sprintf("%s/05-results/02-trait-models/04-pred", wd) %>% list.files()) %>%
  mutate(pred_rx = map2(file, "rx_pred", loadRData)) %>%
  separate(file, c("trait", "idio_metric", "idio_wave"), sep = "-") %>%
  mutate(idio_wave = str_remove_all(idio_wave, ".RData")) %>%
  unnest(pred_rx) 
```

```{r}
sing_trait_traj_rx_fun <- function(d, trait, metric, wave){
  lim <- c(floor(min(d$Estimate)-1.5), ceiling(max(d$Estimate) + 1.5))
  p <- d %>%
    ggplot(aes(x = wave_c + 1, y = Estimate, color = idio_value)) + 
      # geom_ribbon(aes(ymin = `Q2.5`, ymax = `Q97.5`, fill = idio_fac), alpha = .25) + 
      geom_line(aes(group = SID), size = .2) + 
      stat_smooth(method = "lm"
                  , formula = y ~ x
                  , size = .6
                  , color = "black") +
      scale_x_continuous(
        limits = c(1,7)
        , breaks = seq(1, 7)
      ) +
      scale_y_continuous(
        limits = lim
        , breaks = seq(lim[1], lim[2], 2)
      ) +
      scale_color_gradient(
        low = "seagreen1"
        , high = "seagreen4"
      ) +
      labs(
        x = "Wave"
        , y = "Estimated Trait Level"
        # , color = metric
        , color = metric
        # , linetype = metric
        ) + 
      theme_classic() + 
    theme(
      strip.background = element_rect(fill = "black")
      , strip.text = element_text(face = "bold", color = "white", size = rel(1.2))
      , legend.text = element_text(face = "bold")
      , legend.position = "bottom"
      , legend.title = element_text(face = "bold")
      , axis.text = element_text(face = "bold")
      , axis.title = element_text(face = "bold")
      , panel.background = element_rect(color = "black", size = rel(3))
    )
  ggsave(p
         , file = sprintf("%s/05-results/04-plots/01-trait/02-px-trajectories/%s-%s-%s.png"
                          , wd, trait, metric, wave)
         , width = 7
         , height = 4)
  ggsave(p
         , file = sprintf("%s/05-results/04-plots/01-trait/02-px-trajectories/%s-%s-%s.pdf"
                          , wd, trait, metric, wave)
         , width = 7
         , height = 4)
  return(p)
}


nested_pred_plots <- nested_pred_rx %>%
    mutate(trait = factor(trait, c("E", "A", "C", "N", "O")
                          , c("Extraversion", "Agreeableness", "Conscientiousness", "Neuroticism", "Openness"))) %>%
  group_by(idio_metric, idio_wave, trait) %>%
  nest() %>%
  ungroup() %>%
  mutate(p_traj = pmap(list(data, trait, idio_metric, idio_wave), sing_trait_traj_rx_fun))
```



# Consistency Trajectories  
## Merge the Data  
```{r}
d_nested <- trait_rs %>%
  mutate(SID = as.character(SID)) %>%
  full_join(
    idio_long %>% 
      rename(i_wave = wave)
  )  %>% 
  filter(!is.na(i_wave)) %>%
  group_by(i_wave, idio_index) %>%
  nest() %>%
  ungroup()
```

## Sample Model  
```{r}
d <- d_nested$data[[1]]
f <- bf(r ~ 1 - (1 - intercept)*exp(-asymptote*wave_c),
               nonlinear = intercept ~ 1 + idio_value + (1 | i | SID), 
               asymptote ~ 1 + idio_value + (1  | i | SID),
               nl = T)
get_prior(f, data = d, family = gaussian())

m0 <- brm(
  formula = f
  , data = d
  , init = 0
  , prior = c(prior(normal(.6, .1), class = b, coef = "Intercept", nlpar = "intercept"),
                                 prior(cauchy(0, .1), class = sd, nlpar = "intercept"),
                                 prior(normal(0, .1), class = b, nlpar = "intercept"),
                                 prior(cauchy(0, .1), class = sd, nlpar = "asymptote"),
                                 prior(normal(0, .1), class = b, nlpar = "asymptote"),
                                 # prior(exponential(1), class = sigma),
                                 prior(lkj(1), class = cor))
  , family = gaussian()
  , cores = 4
  , chains = 4
  , iter = 100
  , warmup = 10
  )


save(m0, file = sprintf("%s/05-results/trait-sample-model.RData", wd))
```

## Run the Models  
```{r}
nonlin_model_fun <- function(d, metric, wave){
  m <- update(m0
              , newdata = d
              # , prior = c(prior(normal(.6, .1), class = Intercept)
              #             , prior(cauchy(0, .1), class = sd)
              #             , prior(normal(0, .1), class = b)
              #             , prior(exponential(1), class = sigma)
              #             , prior(lkj(1), class = cor))
              , cores = 4
              , chains = 4
              , iter = 8000
              , warmup = 3000
  )
  save(m, file = sprintf("%s/05-results/03-r-models/01-models/%s-%s.RData", wd, metric, wave))
  
  fx <- tidy(m)
  rx <- coef(m)$SID %>% array_tree(3) %>% 
    tibble(term = names(.), data = .) %>%
    filter(!grepl("idio_value", term)) %>%
    mutate(data = map(data, ~(.) %>% data.frame %>% 
                        rownames_to_column("SID"))) %>% 
    unnest(data) %>% 
    select(term, SID, estimate = Estimate, conf.low = Q2.5, conf.high = Q97.5)
  save(fx, rx, file = sprintf("%s/05-results/03-r-models/02-summary/%s-%s.RData", wd, metric, wave))
  
  draws <- as_draws_df(m)
  save(draws, file = sprintf("%s/05-results/03-r-models/03-draws/%s-%s.RData", wd, metric, wave))
  
  idio_levs <- d %>% 
    select(SID, idio_value) %>%
    distinct() %>%
    drop_na() %>%
    summarize(m = mean(idio_value)
              , low = m - sd(idio_value)
              , high = m + sd(idio_value))
  
  frame <- crossing(
    wave_c = 0:6
    , idio_value = c(idio_levs$low, idio_levs$m, idio_levs$high)
  ) %>%
    mutate(idio_fac = factor(idio_value, c(idio_levs$low, idio_levs$m, idio_levs$high), c("-1 SD", "M", "+1 SD"))) 
  fx_pred <- bind_cols(frame, fitted(m, newdata = frame, re_formula = NA))
  
  frame <- m$data %>% 
    select(SID, wave_c, idio_value) %>%
    distinct()
  rx_pred <- bind_cols(frame, fitted(m, newdata = frame))
  save(fx_pred, rx_pred, file = sprintf("%s/05-results/03-r-models/04-pred/%s-%s.RData", wd, metric, wave))
  
  rm(list = ls())
  gc()
  return(T)
}

d_nested %>%
  mutate(m = pmap(list(data, idio_index, i_wave), nonlin_model_fun))
```

## Compile the Results  
### Tables  
```{r}
loadRData <- function(file, obj){
    #loads an RData file, and returns it
    path <- sprintf("%s/05-results/03-r-models/02-summary/%s", wd, file)
    load(path)
    get(ls()[grepl(obj, ls())])
}

nested_fx_r <- tibble(file = sprintf("%s/05-results/03-r-models/02-summary", wd) %>% list.files()) %>%
  mutate(fx = map2(file, "fx", loadRData)) %>%
  separate(file, c("idio_metric", "idio_wave"), sep = "-") %>%
  mutate(idio_wave = str_remove_all(idio_wave, ".RData")) %>%
  unnest(fx) %>%
  filter(effect == "fixed") 
  mutate(sig = ifelse(sign(conf.low) == sign(conf.high), "sig", "ns"))
  group_by(idio_metric, idio_wave) %>%
  nest() %>%
  ungroup()
  
tab <- nested_fx_r %>%
  filter(idio_metric == "density" & idio_wave == "S4") %>%
  mutate(sig = ifelse(sign(conf.low) == sign(conf.high), "sig", "ns")) %>%
  mutate_at(vars(estimate, conf.low, conf.high), ~sprintf("%.2f", .)) %>%
  mutate(CI = sprintf("[%s, %s]", conf.low, conf.high)) %>%
  mutate_at(vars(estimate, CI), ~ifelse(sig == "sig", sprintf("<strong>%s</strong>", .), .)) %>%
  select(idio_metric, term, estimate, CI) %>%
  kable(.
        , "html"
        , escape = F
        , col.names = c("Metric", "Term", "Est.", "CI")
        , align = c("c", "l", "c", "c")) %>%
  kable_classic(full_width = F)

save_kable(tab, file = sprintf("%s/05-results/05-tables/tab-2.html", wd))
```


```{r}
load("/Volumes/Emorie/projects/linking-change/05-results/03-r-models/01-models/density-S4.RData")
d <- m$data
idio_levs <- d %>% 
    select(SID, idio_value) %>%
    distinct() %>%
    drop_na() %>%
    summarize(m = mean(idio_value)
              , low = m - sd(idio_value)
              , high = m + sd(idio_value))

hyp_test <- hypothesis(m
           , c("asymptote_Intercept + 0.3763668*asymptote_idio_value = 0"
               , "asymptote_Intercept + 0.1349899*asymptote_idio_value = 0"
               , "asymptote_Intercept + 0.6177438*asymptote_idio_value = 0"))

hyp_test$hypothesis 
```

### Plots  
#### Random Effects Distributions  
```{r}
loadRData <- function(file, obj){
    #loads an RData file, and returns it
    path <- sprintf("%s/05-results/02-trait-models/02-summary/%s", wd, file)
    load(path)
    get(ls()[grepl(obj, ls())])
}

nested_rx <- tibble(file = sprintf("%s/05-results/02-trait-models/02-summary", wd) %>% list.files()) %>%
  mutate(rx = map2(file, "rx", loadRData)) %>%
  separate(file, c("trait", "idio_metric", "idio_wave"), sep = "-") %>%
  mutate(idio_wave = str_remove_all(idio_wave, ".RData")) %>%
  unnest(rx) %>%
  mutate(trait = factor(trait, c("E", "A", "C", "N", "O")
          , c("Extraversion", "Agreeableness", "Conscientiousness", "Neuroticism", "Openness"))) %>%
  group_by(idio_metric, idio_wave, term, trait) %>%
  nest() %>%
  ungroup()
```

```{r}
rx_est_fun <- function(d, trait){
  ord <- (d %>% arrange(desc(estimate)))$SID
  d %>%
    mutate(SID = factor(SID, levels = ord)
           , sig = ifelse(sign(conf.low) == sign(conf.high), "sig", "ns")) %>%
    ggplot(aes(x = SID, y = estimate)) + 
      geom_errorbar(aes(ymin = conf.low, ymax = conf.high)
                    , position = "dodge"
                    , width = 0
                    , size = .25) +
      geom_point(size = .5) + 
      labs(x = "SID"
           , y = "Estimated Trait Level"
           , title = trait) +
      coord_flip() + 
      theme_classic() + 
      theme(legend.position = "bottom"
            , plot.title = element_text(face = "bold", hjust = .5)
            , axis.text.y = element_blank())
}

nested_rx_plots <- nested_rx %>%
  mutate(p = map2(data, trait, rx_est_fun)) %>%
  group_by(idio_metric, idio_wave, term) %>%
  nest() %>% 
  ungroup()

comb_trait_plot_fun <- function(d){
  d <- d %>% arrange(trait)
  p1 <- d$p[[1]]; p2 <- d$p[[2]]; p3 <- d$p[[3]]; p4 <- d$p[[4]]; p5 <- d$p[[5]]
  p1 <- p1 +  labs (y = " "); p2 <- p2 +  labs (y =" ")
  p4 <- p4 +  labs (y = " "); p5 <- p5 +  labs (y = " ")
  plot_grid(p1, p2, p3, p4, p5
            , nrow = 1
            , axis = "tb"
            , align = "v")
}

nested_rx_plots <- nested_rx_plots
```


#### Trajectories  
##### Fixed Effects  
```{r}
loadRData <- function(file, obj){
    #loads an RData file, and returns it
    path <- sprintf("%s/05-results/03-r-models/04-pred/%s", wd, file)
    load(path)
    get(ls()[grepl(obj, ls())])
}

nested_pred_r <- tibble(file = sprintf("%s/05-results/03-r-models/04-pred", wd) %>% list.files()) %>%
  mutate(pred_fx = map2(file, "fx_pred", loadRData)) %>%
  separate(file, c("idio_metric", "idio_wave"), sep = "-") %>%
  mutate(idio_wave = str_remove_all(idio_wave, ".RData")) %>%
  unnest(pred_fx) %>%
  group_by(idio_metric, idio_wave) %>%
  nest() %>%
  ungroup()
```

```{r}
ip_traj_fun <- function(d, metric, wave){
  p <- d %>%
    # mutate(trait = factor(trait, c("E", "A", "C", "N", "O")
    #                       , c("Extraversion", "Agreeableness", "Conscientiousness", "Neuroticism", "Openness"))) %>%
    ggplot(aes(x = wave_c + 1, y = Estimate, group = idio_fac)) + 
      geom_ribbon(aes(ymin = `Q2.5`, ymax = `Q97.5`, fill = idio_fac), alpha = .25) + 
      geom_line(aes(linetype = idio_fac), color = "black", size = .6) + 
      scale_x_continuous(
        limits = c(1,6)
        , breaks = seq(1, 6)
        , labels = c("1-2", "2-3", "3-4", "4-5", "5-6", "6-7")
      ) +
      scale_y_continuous(
        limits = c(.5,1)
        , breaks = seq(.5, 1, .1)
      ) +
      labs(
        x = "Wave"
        , y = "Estimated Ipsative Consistency"
        , color = metric
        , fill = metric
        , linetype = metric
        ) + 
      # facet_wrap(~idio_metric) +
      theme_classic() + 
    theme(
      strip.background = element_rect(fill = "black")
      , strip.text = element_text(face = "bold", color = "white", size = rel(1.2))
      , legend.text = element_text(face = "bold")
      , legend.position = "bottom"
      , legend.title = element_text(face = "bold")
      , axis.text = element_text(face = "bold")
      , axis.title = element_text(face = "bold")
      , panel.background = element_rect(color = "black", size = rel(3))
    )
  ggsave(p
         , file = sprintf("%s/05-results/04-plots/02-consistency/01-trajectories/%s-%s.png"
                          , wd, metric, wave)
         , width = 7
         , height = 4)
  ggsave(p
         , file = sprintf("%s/05-results/04-plots/02-consistency/01-trajectories/%s-%s.pdf"
                          , wd, metric, wave)
         , width = 7
         , height = 4)
  return(p)
}

nested_pred_r <- nested_pred_r %>%
  mutate(p_traj = pmap(list(data, idio_metric, idio_wave), ip_traj_fun))

```

##### Random Effects  

```{r}
loadRData <- function(file, obj){
    #loads an RData file, and returns it
    path <- sprintf("%s/05-results/03-r-models/04-pred/%s", wd, file)
    load(path)
    get(ls()[grepl(obj, ls())])
}

nested_pred_rx <- tibble(file = sprintf("%s/05-results/03-r-models/04-pred", wd) %>% list.files()) %>%
  mutate(pred_rx = map2(file, "rx_pred", loadRData)) %>%
  separate(file, c("idio_metric", "idio_wave"), sep = "-") %>%
  mutate(idio_wave = str_remove_all(idio_wave, ".RData")) %>%
  unnest(pred_rx) 
```


```{r}
sing_trait_traj_rx_fun <- function(d, metric, wave){
  # lim <- c(floor(min(d$Estimate)-1.5), ceiling(max(d$Estimate) + 1.5))
  p <- d %>%
    ggplot(aes(x = wave_c + 1, y = Estimate, color = idio_value)) + 
      # geom_ribbon(aes(ymin = `Q2.5`, ymax = `Q97.5`, fill = idio_fac), alpha = .25) + 
      geom_line(aes(group = SID), size = .2) + 
      stat_smooth(method = "lm"
                  , formula = y ~ x
                  , size = .6
                  , color = "black") +
      scale_x_continuous(
        limits = c(1,6)
        , breaks = seq(1, 6)
        , labels = c("1-2", "2-3", "3-4", "4-5", "5-6", "6-7")
      ) +
      scale_y_continuous(
        limits = c(.4, 1)
        , breaks = seq(.4, 1, .2)
      ) +
      scale_color_gradient(
        low = "seagreen1"
        , high = "seagreen4"
      ) +
      labs(
        x = "Wave"
        , y = "Estimated Trait Level"
        # , color = metric
        , color = metric
        # , linetype = metric
        ) + 
      theme_classic() + 
    theme(
      strip.background = element_rect(fill = "black")
      , strip.text = element_text(face = "bold", color = "white", size = rel(1.2))
      , legend.text = element_text(face = "bold")
      , legend.position = "bottom"
      , legend.title = element_text(face = "bold")
      , axis.text = element_text(face = "bold")
      , axis.title = element_text(face = "bold")
      , panel.background = element_rect(color = "black", size = rel(3))
    )
  ggsave(p
         , file = sprintf("%s/05-results/04-plots/02-consistency/02-px-trajectories/%s-%s.png"
                          , wd, metric, wave)
         , width = 7
         , height = 4)
  ggsave(p
         , file = sprintf("%s/05-results/04-plots/02-consistency/02-px-trajectories/%s-%s.pdf"
                          , wd, metric, wave)
         , width = 7
         , height = 4)
  return(p)
}


nested_pred_plots <- nested_pred_rx %>%
  group_by(idio_metric, idio_wave) %>%
  nest() %>%
  ungroup() %>%
  mutate(p_traj = pmap(list(data, idio_metric, idio_wave), sing_trait_traj_rx_fun))
```

